### 2020-02-22 main_text/main_text.tex
Add fig w/ real data from GC + minor edits from KL

	\section*{Experimental motivation} \label{sec:experiment}
	Our work was motivated by the experimental observation of bimodality in the \emph{xap} circuit, which is shown in Fig~\ref{fig1:data}. We focus on the essential findings here and refer the reader to~\nameref{S1_Text} for more experimental details. Briefly, we placed a fluorescent reporter under the control of the wild type (wt) \emph{xapAB} promoter. This construct was placed in three different backgrounds: \textDelta\emph{xapABR}, \textDelta\emph{xapAB}, and wt. Fig~\subref{fig1:data}{A} shows that for increasing xanthosine concentration, expression in the wt-background increases in a switch-like way: it is nearly zero when there is little xanthosine (``uninduced state''), but increases drastically when there is more (``induced state''). In between, the aforementioned bimodal distribution is obtained, where some bacteria are in the uninduced expression state and others are induced. \textcolor{red}{maybe remove: In addition, we observed that the property of being induced seems to be passed on to daughter cells, suggesting that there is not merely bimodality, but bistability.}

	\begin{figure}%[h!]
		\centering
		\includegraphics[width=0.4\textwidth]{media/Fig1_data.pdf}
		\caption{{\bf Experimental data on the \emph{xap} circuit.} The expression of the \emph{xapAB} promoter was measured for different concentrations of xanthosine in the bacteria's environment. (A) shows the wild type circuit while in (B) the genes \emph{xapABR} and in (C) the genes \emph{xapAB} are removed. The wild type circuit behaves like a switch. \textcolor{red}{placeholder figure up to now}}
		\label{fig1:data}
	\end{figure}

@@

	Clearly, XapR regulates the \emph{xapAB} promoter. As mentioned in the introduction, there are two binding sites for XapR on the \emph{xapAB} promoter: one directly at the polymerase binding site and one further upstream. When the upstream binding site is removed, bimodality is lost and the expression of \emph{xapAB} becomes several orders of magnitude weaker, as can be seen in Fig~\ref{}.
	\textcolor{red}{data missing}

@@

	\paragraph*{Time evolution and adaptation times.}
	Fig~\subref{fig9:StochT}{A} shows the time evolution of the protein concentration for one typical run of the simulation.
	Again, the simulation was started with a mRNA, protein and intracellular
	xanthosine count of 0 and was run for a simulated time of $5 \cdot 10^5
	\unit{s}$. In this specific example, the fixed point was reached after roughly $1.5 \cdot 10^5
	\unit{s}$ (adaptation time). This time varies: Fig~\subref{fig9:StochT}{B} shows the distribution of adaptation times from 1000 runs of the simulation. In both figures, the trajectory obtained from integrating the deterministic system is shown for comparison. It clearly agree well with the simulation on average.

@@

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of deterministic fixed points, while the dashed line indicates the instability of the middle one. The orange and yellow points show the mean in the stochastic simulations when started at zero and at the high fixed point, respectively. The positions of the two peaks in the bimodal distributions are indicated by smaller points, connected by dotted lines. The arrows illustrate the hysteresis loop in the stochastic simulations.}
		\label{fig10:Bifurcation}
	\end{figure}

>>>>

	\section*{Experimental motivation} \label{sec:experiment}
	Our work was motivated by the experimental observation of bimodality
	in the \emph{xap} circuit, which is shown in Fig~\ref{fig1:data}. We
	focus on the essential findings here and refer the reader
	to~\nameref{S1_Text} for more experimental details. Briefly, we
	placed a fluorescent reporter under the control of the wild type
	(wt) \emph{xapAB} promoter. This construct was placed in three
	different backgrounds: \textDelta\emph{xapABR},
	\textDelta\emph{xapAB}, and wt. The right panel of
	Fig~\subref{fig1:data}{A} shows that for increasing xanthosine
	concentration, expression in the wt-background increases in a
	switch-like way: it is nearly zero when there is little xanthosine
	(``uninduced state''), but increases drastically when there is more
	(``induced state''). In between, the aforementioned bimodal
	distribution is obtained, where some bacteria are in the uninduced
	expression state and others are induced.

	\begin{figure}%[h!]
		\centering
		\includegraphics[width=1\textwidth]{media/Fig1_data.eps}
		\caption{{\bf Experimental data on the \emph{xap} circuit.}
		(A) The expression of the \emph{xapAB} promoter was measured for
		different concentrations of xanthosine in the bacteria's
		environment. The right panel shows the wild type circuit while
		on the left the genes \emph{xapABR} and in the middle the genes
		\emph{xapAB} are removed. The wild type circuit behaves like a
		switch. Note that the fluorescence scales of the middle panel
		and the other two are not comparable.
		(B) The fold-change in gene expression upon addition of
		xanthosine for the wt promoter and for the promoter with only
		the XapR binding site right at the polymerase binding site.
		}
		\label{fig1:data}
	\end{figure}

@@

	Clearly, XapR regulates the \emph{xapAB} promoter. As mentioned in
	the introduction, there are two binding sites for XapR on the
	\emph{xapAB} promoter: one directly at the polymerase binding site
	and one further upstream. When the upstream binding site is removed,
	bimodality is lost and the activation of the \emph{xapAB}-expression
	by xanthosine (via XapR) becomes negligible, as can be seen in
	Fig~\subref{fig1:data}{B}.

@@

	\paragraph*{Time evolution and adaptation times.}
	Fig~\subref{fig9:StochT}{A} shows the time evolution of the protein concentration for one typical run of the simulation.
	Again, the simulation was started with a mRNA, protein and intracellular
	xanthosine count of 0 and was run for a simulated time of $5 \cdot 10^5
	\unit{s}$. In this specific example, the fixed point was reached after roughly $1.5 \cdot 10^5
	\unit{s}$ (adaptation time).
	This time varies: Fig~\subref{fig9:StochT}{B} shows the distribution
	of adaptation times from 1000 runs of the simulation (where we
	neglected the around 10 runs with adaptation times larger than $6
	\cdot 10^5 \unit{s}$). In both figures, the trajectory obtained from
	integrating the deterministic system is shown for comparison. It
	clearly agree well with the simulation on average.

@@

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of the deterministic fixed
			points, while the dashed line indicates the instability of
			the middle one. The orange and yellow points show the mean
			of the stochastic simulations when started at zero and at
			the high fixed point, respectively. The positions of the two
			peaks in the bimodal distributions are indicated by smaller
			points, connected by dotted lines. The arrows illustrate the
			hysteresis loop in the stochastic simulations.
			}
		\label{fig10:Bifurcation}
	\end{figure}

### 2020-02-22 s1_text/s1_text.tex
Add fig w/ real data from GC + minor edits from KL

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{FigSI6_7.pdf}
	\caption{{\bf Time evolution and adaptation times from the stochastic simulation when transcriptional bursting is included.}
		(A) shows the time evolution from one run of the simulation. The simulation was run once for $5 \cdot 10^5 \unit{s}$ and started
		at an mRNA, protein and intracellular xanthosine count of 0. The parameters that were used are the same as in the
		table in the main text, the only exception being the
		extracellular xanthosine concentration, which was chosen to be
		$\n{[c]_a} = 25$ (recall $\n{[c]_{a}} \defeq \frac{c}{K_{\n{a}}}$,
		$K_{\n{a}} = 5 \cdot 10^{-5} \unit{M}$). (B) Blue shows the time until 90\% of the protein concentration at the upper fixed point was reached in 200 runs of the simulation (same conditions as (A)). The distribution from the main text (without bursting) is shown in orange for comparison. \textcolor{red}{will add some more runs, but the simulation takes forever}}
	\label{evolbursts}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{FigSI6_7.pdf}
	\caption{{\bf Time evolution and adaptation times from the stochastic simulation when transcriptional bursting is included.}
		(A) shows the time evolution from one run of the simulation. The simulation was run once for $5 \cdot 10^5 \unit{s}$ and started
		at an mRNA, protein and intracellular xanthosine count of 0. The parameters that were used are the same as in the
		table in the main text, the only exception being the
		extracellular xanthosine concentration, which was chosen to be
		$\n{[c]_a} = 25$ (recall $\n{[c]_{a}} \defeq \frac{c}{K_{\n{a}}}$,
		$K_{\n{a}} = 5 \cdot 10^{-5} \unit{M}$).
		(B) Blue shows the time until 90\% of the protein concentration
		at the upper fixed point was reached in 1000 runs of the
		simulation (same conditions as (A)). The distribution from the
		main text (without bursting) is shown in orange for comparison.
		For both, the mean of the distribution is indicated by the line
		in the corresponding color.
		}
	\label{evolbursts}
\end{figure}
